---
title: "Untitled"
author: "Tanya Panesar"
date: "16/04/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r}
getwd()
```

```{r}
IAT_data <- read.csv("IAT_ogcsv.csv", header = TRUE)
read.table("IAT_ogcsv.csv", header = TRUE, sep = ",")
```


```{r}

IAT_data <- IAT_data

str(IAT_data)
```

The following is the mean: 

```{r}
mean(IAT_data$Positive.Word.Reaction.Time.Average)
mean(IAT_data$Sum.of.Positive.Reaction.Time)
mean(IAT_data$No.of.correct.keystorks)
mean(IAT_data$Negative.Word.Reaction.Time.Average)
mean(IAT_data$Sum.of.Negative.Reaction.Time)
mean(IAT_data$No.of.correct.keystorks.1)
```

The following is the standard deviation: 

```{r}
sd(IAT_data$Positive.Word.Reaction.Time.Average)
sd(IAT_data$Sum.of.Positive.Reaction.Time)
sd(IAT_data$No.of.correct.keystorks)
sd(IAT_data$Negative.Word.Reaction.Time.Average)
sd(IAT_data$Sum.of.Negative.Reaction.Time)
sd(IAT_data$No.of.correct.keystorks.1)
```

Below is the median: 
```{r}
median(IAT_data$Positive.Word.Reaction.Time.Average)
median(IAT_data$Sum.of.Positive.Reaction.Time)
median(IAT_data$No.of.correct.keystorks)
median(IAT_data$No.of.correct.keystorks)
median(IAT_data$Sum.of.Negative.Reaction.Time)
median(IAT_data$No.of.correct.keystorks.1)
```


Here is the summary of all the rows: Block, Positive.Word.Reaction.Time.Average,  Sum.of.Positive.Reaction.Time, No.of.correct.keystorks, Negative.Word.Reaction.Time.Average Sum.of.Negative.Reaction.Time, No.of.correct.keystorks.1 and Names. It includes minimum, 1st quadrant, mean, median, 3rd quadrant and maximum. 

```{r}
summary(IAT_data)
```


```{r}
names(IAT_data)

```

```{r plot}
IAT_data %>%
  ggplot(aes(x = Positive.Word.Reaction.Time.Average, y = Negative.Word.Reaction.Time.Average,  color = as.factor(Block))) + geom_point()

```

```{r t_test, echo = FALSE, include = FALSE}


data_block.3 <- IAT_data %>%
  filter(Block == "3")
data_block.5 <- IAT_data %>%
  filter(Block == "5")

ttest.1 <- t.test(data_block.3$Positive.Word.Reaction.Time.Average, data_block.5$Negative.Word.Reaction.Time.Average,paired=TRUE)

ttest.2 <- t.test(data_block.3$Positive.Word.Reaction.Time.Average, data_block.5$Negative.Word.Reaction.Time.Average,paired = TRUE)

ttest.1
ttest.2
```

```{r}
#install.packages("tidyverse")
library(papaja)
library(tidyverse)
```

```{r}
#install.packages("ggplot.multistats")
#install.packages("ggplot2")
  
```


